Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion-Proof.tex

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
$\pfedit{O \left(\ARMNUM^2 /p \right)}$
and expected regret bounded above by \pfedit{$O(\ARMNUM / p)$}.
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\pfedit{
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
}
\right).
$
%\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.

To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with \pfdelete{simply} $2/\MinProb$ \pfedit{and use $L=0$.}
In return, the length of phase $s$ is now bounded only by $\ARMNUM s$ instead of $\ARMNUM \log(s)$, \pfedit{and the expectetd number of times steps in which a payment is made is bounded by $O(N/p + N^2)$.}
Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the bound $O(R(N/p + N^2) + NR + NR) = O(N/p)$ since $p \le 1/N$.

\pfcomment{
The calculation I did for the bound on the expected payment is,
\begin{align*}
&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{\frac{2}{p},
    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
    \bigg\}
\right)
\end{align*}
}

\pfcomment{
The calculation I did for the bound on the regret is:

\begin{itemize}
\item regret from times when we pay is $RN(N + 1/p)$
\item regret from phases with $\gamma(s) >= \hat{z}$ is $O(NR D^6 d^6 \sigma^6 / \hat{z}^6)$
\item regret from pulls with small regret is 0
\item regret from pulls with big regret is $O(NR)$
\end{itemize}
}

\end{proof}

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
has expected payment bounded above by 
$O \left(\ARMNUM^2/\MinProb \right)$
and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of
Theorem~\ref{rst:budget},
except that we now define
$h(\ell) := \max \left( \frac{2}{\MinProb},
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2} \right)$.
%\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.

To prove the bound on the expected regret,
one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with $2/\MinProb$ and use $L=0$.
In return, the length of phase $s$ is now bounded only by $\ARMNUM s$
instead of $\ARMNUM \log(s)$,
and the expectetd number of times steps in which a payment is made is bounded by
$O(\ARMNUM/\MinProb + \ARMNUM^2)$.
Substituting these changes into the proof of Theorem~\ref{rst:regret},
we obtain the bound $O(\MAXR(\ARMNUM/\MinProb + \ARMNUM^2) + \ARMNUM \MAXR +
\ARMNUM \MAXR) = O(\ARMNUM/\MinProb)$ since $\MinProb \le 1/\ARMNUM$.
\end{proof}

% \pfcomment{
% The calculation I did for the bound on the expected payment is,
% \begin{align*}
% &O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
% &=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
%     \max\bigg\{\frac{2}{p},
%     \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
%     \bigg\}
% \right)
% \end{align*}
% }
% \pfcomment{
% The calculation I did for the bound on the regret is:

% \begin{itemize}
% \item regret from times when we pay is $RN(N + 1/p)$
% \item regret from phases with $\gamma(s) >= \hat{z}$ is $O(NR D^6 d^6 \sigma^6 / \hat{z}^6)$
% \item regret from pulls with small regret is 0
% \item regret from pulls with big regret is $O(NR)$
% \end{itemize}
% }
